SHARP - II. Mass structure in strong lenses is not necessarily dark matter substructure: A flux ratio anomaly from an edge-on disc in B1555+375

### 2016-07-11 papers/B1555_EdgeOn/Resubmission_v3/B1555_EdgeOn.tex
prepare to do realization valid test

The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B. \textbf{An exponential disc component is added to the smooth lens model. Former study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$). A detailed definition of these mass profiles is described by \citet{Kee01}. The source position adds two additional model parameters. 
%We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
%An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}

@@

\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.} The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.  We find that adding an elongated exponential disc to a smooth SIE model \textbf{successfully reproduces the flux ratio anomaly in this system}. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the disc component makes up about 15 per cent of the total projected mass within the Einstein radius.
% (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. 
\textbf{While} investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent \citep{swells1,swells3,swells6}.
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.

>>>>

The next step is to test if a physically plausible edge-on disc can cause a perturbation in the strong lensing mass model that produces the observed flux ratio anomaly of  merging images A and B. \textbf{An exponential disc component is added to the smooth lens model. Previous study has shown that exponential disc profile best describes the light distribution of the disc component in spiral galaxies \citep{Kee98}.} The free parameters of this model are the SIE Einstein radius ($b$), centroid position, ellipticity ($e = 1 - q$), position angle ($\theta$), the exponential disc intrinsic central density ($\kappa_0$) and scale length ($R_s$). A detailed definition of these mass profiles is described by \citet{Kee01}. The source position adds two additional model parameters. 
%We have not included a third component such as an external shear or additional NFW halo term because the number of constraints provided by the compact images detected by MERLIN is not sufficient to constrain such a model.
%An SIE profile is also sufficient to include the halo mass since B1555 has a small Einstein radius.}

@@

\textbf{Our model predicted results are shown in Table \ref{tab:results} with comparison to the observed data and the single SIE lens model.} The best-fit model parameters and 68 per cent confidence level (CL) errors are listed in Table~\ref{tab:model}, and the lens model is illustrated in Fig.~\ref{fig:3panel}c.  We find that adding an elongated exponential disc to a smooth SIE model \textbf{successfully reproduces the flux ratio anomaly in this system}. 
% with a reduced $\chi^2 = 2.7$
The positions are all in agreement, and the flux ratios are consistent at the $2\sigma$ level, with excellent agreement now obtained for the two merging images A and B. The remaining differences in the fluxes may be due to the real lensed source being slightly extended rather than the point source that we used in our model. The model requires that the disc component makes up about 15 per cent of the total projected mass within the Einstein radius.
% (1.7~kpc for an assumed lens redshift of $z_l = 1$ but the mass fraction is independent of the lens and source redshifts since this ratio is independent of distance).  In this central region of an edge-on spiral galaxy, the baryonic mass can be a significant component of the total projected mass. 
Investigations of edge-on spiral lenses, for example from the SWELLS survey, show that the disc mass fraction within the Einstein radius ranges from 5 to 30 per cent \citep{swells1,swells3,swells6}.
%In the NIR imaging there is no sign of a bulge; a bulge plus disk fit to the lens galaxy surface brightness distribution gives a bulge component that is consistent with zero emission.  We therefore interpret the ExpDisc component as a good description of the baryonic mass of the lens galaxy. 
%We note that there is a significant 0.036~arcsec offset between the SIE and ExpDisc components, which is likely due to an additional ellipticity in the model (e.g. from an external shear) that is being partly compensated for by the disc component. Again, more complex mass models require the stronger constraints provided by deep imaging of the full extent of the gravitational arc in future high resolution radio observations.
